Gap formation and stability in non-isothermal protoplanetary discs

### 2015-03-27 paper/model.tex
updating

\begin{align}\label{initial_density}
   \Sigma(r) = \Sigma_\mathrm{ref}\left(\frac{r}{r_\mathrm{in}}\right)^{-s}
    \left[1 - \sqrt{\frac{r_\mathrm{in}}{r + H_i(\rin)}}\,\right] 
\end{align}
where the power-law index $s=2$, $H(r) = \ciso\Omega_k $ defines the disc scale-height 
where $\ciso=\sqrt{p/\Sigma}$ isothermal sound-speed. The disc aspect ratio is defined as $h\equiv H/r$ and initially
$h=0.05$. For a non-self-gravitating disc, the surface density scale
$\Sigma_\mathrm{ref}$ is arbitrary.

>>>>

\begin{align}\label{initial_density}
   \Sigma(r) = \Sigma_\mathrm{ref}\left(\frac{r}{r_\mathrm{in}}\right)^{-s}
    \left[1 - \sqrt{\frac{r_\mathrm{in}}{r + H_i(\rin)}}\,\right] 
\end{align}
where the power-law index $s=2$, $H(r) = \ciso\Omega_k $ defines the disc scale-height 
where $\ciso=\sqrt{p/\Sigma}$ is the isothermal sound-speed. The disc aspect ratio is defined as $h\equiv H/r$ and initially
$h=0.05$. For a non-self-gravitating disc, the surface density scale
$\Sigma_\mathrm{ref}$ is arbitrary.

### 2015-03-27 paper/results.tex
updating

{\bf For completeness we also simulated a locally
  isothermal disk with $\epsilon=0.05$ where the
  sound-speed is kept strictly equal to its initial value.  This
  simulation yield a most unstable growth rate
  $\sigma/\Omega(r_p)\simeq 0.05$ at $m=5$,   
  compared with a value of $0.085$ at $m=6$ for a corresponding
  simulation that includes the energy equation but with rapid cooling
  $\tilde{\beta}=0.01$. However, the vortex evolution is similar.}

@@

{\bf We comment here that a locally isothermal simulation, where the
  disc sound-speed is kept constant in time, was also
  performed for comparison. In this case we did not observe
  significant vortex decay within the simulation timescale
 (implying $t_\mathrm{diss}\gtrsim2000P_0$).  We expect the corresponding vortex
 lifetime to exceed that for $\tilde{\beta}=0.01$. Including an energy
 equation, even with rapid cooling (or setting $\gamma$ close to 
 unity), could still lead to discrepancies with a locally isothermal disc. This is 
 due to the advection-creation of specific entropy within the planet's horseshoe
 region with the former case,  thereby affecting the generalized vortensity 
 and therefore the instability (\S\ref{linear}) and subsequent vortex evolution. 
 Nevertheless, a longer vortex 
 lifetime at the gap edge in a locally isothermal disk would 
 be consistent with the above trend of increasing vortex lifetimes as
 $\tilde{\beta}\to0$.}

>>>>

{\bf For completeness we also simulated a locally
  isothermal disc with $h=0.05$ where the
  sound-speed is kept strictly equal to its initial value.  This
  simulation yield a most unstable growth rate
  $\sigma/\Omega(r_p)\simeq 0.05$ at $m=5$,   
  compared with a value of $0.085$ at $m=6$ for a corresponding
  simulation that includes the energy equation but with rapid cooling
  $\tilde{\beta}=0.01$. However, the vortex evolution is similar.}

@@

{\bf We comment here that a locally isothermal simulation, where the
  disc sound-speed is kept constant in time, was also
  performed for comparison. In this case we did not observe
  significant vortex decay within the simulation timescale
 (implying $t_\mathrm{diss}\gtrsim2000P_0$).  We expect the corresponding vortex
 lifetime to exceed that for $\tilde{\beta}=0.01$. Including an energy
 equation with rapid cooling (or setting $\gamma$ close to 
 unity), could still lead to discrepancies with a locally isothermal disc. This is 
 due to the advection-creation of specific entropy within the planet's horseshoe
 region with the former case,  thereby affecting the generalized vortensity 
 and therefore the instability (\S\ref{linear}) and subsequent vortex evolution. 
 Nevertheless, a longer vortex 
 lifetime in a locally isothermal disc would 
 be consistent with the above trend of increasing vortex lifetimes as
 $\tilde{\beta}\to0$.}
